|

### 2016-08-13 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Metadata at top of article

---
author:
fontfamily:
- mathpazo
fontsize: 12pt
output:
  pdf_document:
    fig_caption: True
    md_extensions: '-tex_math_single_backslash'
    number_sections: False
  word_document: 
    fig_caption: True
    md_extensions: '-tex_math_single_backslash'
    pandoc_args: ["--smart"]
title: "The Spine of American Law: Digital Text Analysis and U.S. Legal Practice"
---

@@

>>>>

---
fontfamily:
- mathpazo
fontsize: 12pt
geometry:
- "margin=1in"
output:
  pdf_document:
    fig_caption: True
    md_extensions: '-tex_math_single_backslash'
    number_sections: False
    template: article-template.tex
  word_document: 
    fig_caption: True
    md_extensions: '-tex_math_single_backslash'
    pandoc_args: ["--smart"]
title: |
       | The Spine of American Law\: 
       | Digital Text Analysis and U.S. Legal Practice
author: 
- name: Kellen Funk
  affiliation: Princeton University
  email: kfunk@princeton.edu
- name: Lincoln Mullen
  affiliation: George Mason University
  email: lincoln@lincolnmullen.com
---

@@

*This article is currently under peer review at the American Historical Review.*

\
